---
title: "Attendance Database"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{attn} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE)
library(legco)
```

## Introduction

This database contains the attendance record of LegCo Council and committee open meetings
since the sixth term.

For more details of the database, see <https://www.legco.gov.hk/odata/english/attendance-db.html>.

### Key Identifiers

Here are the key identifies that is useful for locating the neccessary data from the Attendance 
Database:

* `CommitteeID` is the numerical ID of a LegCo committee. It is same as the one in the Meeting
Schedule Database.

* `MeetID` is the numerical ID of a LegCo Council or committee meeting. It is same as the one in the
Meeting Schedule Database.

* `MemberID` is the numerical ID of a LegCo member. It is same as the one in the Meeting Schedule
Database. Note that it is a seperate identifier from the `SpeakerID` of the Hansard Database.

---

This database is accessible with the following function:

## attendance()

`attendance()` fetches the attendance record of one or more LegCo meeting(s), or the attendance record of 
one of more LegCo member(s), or both.

```{r }
# Fetch members who were absent from the Subcommittee on Issues Relating to Bazaars meetings on October 13, 2017
attendance(committee_id = 2704, from = "2017-10-13", to = "2017-10-13", attn = "a")

# Fetch the meetings that Hon Chu Hoi-dick was absent from
v <- attendance(member_id = 910, attn = "a")
head(v)
```
