---
title: "Meeting Attendance Database"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{attn} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(legco)
library(httptest)
start_vignette("attn")
```

## Introduction

This database contains the attendance record of Council and committee open meetings
since the sixth term.

For more details of the database, see <https://www.legco.gov.hk/odata/english/attendance-db.html>.

### Key Identifiers

Here are the key identifies that is useful for locating the necessary data from the Attendance 
Database:

* `CommitteeID` is the numerical ID of a LegCo committee. It is same as the one in the Meeting
Schedule Database.

* `MeetID` is the numerical ID of a Council or committee meeting. It is same as the one in the
Meeting Schedule Database.

* `MemberID` is the numerical ID of a LegCo member. It is same as the one in the Meeting Schedule
Database. Note that it is a separate identifier from the `SpeakerID` of the Hansard Database.

### Total Count

The function in this database has an option to return only the total count of the records matching 
the specified parameters instead of returning the data frame containing the result.
To activate this option, specify `count = TRUE`:

```{r }
# Fetch the total number of members absent from the Council meeting on May 22, 2019
attendance(meet_id = 136897, from = "2019-05-22", to = "2019-05-22", attn = "a", count = TRUE)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

---

This database is accessible with the following function:

## attendance()

`attendance()` fetches the attendance record of one or more LegCo meeting(s), or the attendance record of 
one of more LegCo member(s), or both.

```{r }
# Fetch members who were absent from the Subcommittee on Issues Relating to Bazaars meetings on October 13, 2017
attendance(committee_id = 2704, from = "2017-10-13", to = "2017-10-13", attn = "a")
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```
```{r eval=FALSE}
# Fetch the meetings that Hon Chu Hoi-dick was absent from
v <- attendance(member_id = 776, attn = "a")
head(v)
```
```{r echo=FALSE}
# Fetch the meetings that Hon Chu Hoi-dick was absent from
v <- attendance(member_id = 776, attn = "a", to = "2020-03-27")
head(v)
```
```{r include=FALSE}
end_vignette()
```