---
title: "Bills Database"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bills} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(legco)
library(httptest)
start_vignette("bills")
```

## Introduction

This database contains key information of all the bills that have been presented in LegCo since 1906.

For more details of the database, see <https://www.legco.gov.hk/odata/english/billsdb.html>.

### Key Identifiers

This database has an `InternalKey` which has little value since there is only one data endpoint and 
it is not interchangeable with other databases. To locate the bill in other databases, it is advisable
to use the First, Second and Third Reading dates as the filter parameters (e.g. Hansard database) or 
find the CommitteeID of the relevant bill committee using `legcoplus::search_committee()` from 
the package [legcoplus](https://github.com/elgarteo/legcoplus) (e.g. Meeting Schedule Database).

### Total Count

The function in this database has an option to return only the total count of the records matching 
the specified parameters instead of returning the data frame containing the result.
To activate this option, specify `count = TRUE`:

```{r }
# Fetch the total number of bills that have been discussed in LegCo
all_bills(count = TRUE)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

---

This database is accessible with the following function:

## all_bills()

`all_bills()` fetches the information of bills that have gone through LegCo.

```{r }
# Fetch bills that passed third reading on February 20, 2019
all_bills(third_from = "2019-02-20")
```
```{r include=FALSE}
end_vignette()
```
