---
title: "Hansard Database"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hansard} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(legco)
library(httptest)
start_vignette("hansard")
```

## Introduction

This database contains information on matters discussed in Council meeting since the fifth term
of LegCo. Hinting by its name, the database is built upon the PDF hansard files. Relying on the bookmarks 
and section codes of the hansard files, the data endpoints retrieve data from the files directly. 

For more details of the database, see <https://www.legco.gov.hk/odata/english/hansard-db.html>.

### Key Identifiers

Here are the key identifies that is useful for locating the necessary data from the Hansard database:

* `HansardID` is the numerical ID of a hansard file. A hansard file is the Record of Proceedings of
a Council meeting. Since there are three versions of hansard---Floor Chinese and English, 
each Council meeting has three hansard files, meaning that there are three Hansard IDs corresponding 
to the same meeting.

* `RundownID` is the numerical ID of a rundown in the hansard file. In simple terms, rundowns can be understood 
as individual paragraphs in the Record of Proceedings. 

* `SectionCode` is the alphabetical code stipulating the type of business as indicated in the LegCo Rules of 
Procedures 18(1) that a paragraph text is referring to in the hansard file. 

* `BookmarkName` is the alphabetical code stipulating details of the rundown. A detailed explanation
can be found [here](#rundown).

* `SpeakerID` is the numerical ID stipulating the speaker of a paragraph text in the hansard file.

These identifiers essentially indicate the *when* (HansardID), *where* (RundownID), *what* (SectionCode) 
and *who* (SpeakerID) of a paragraph text in the Record of Proceedings.

### Total Count

All functions in this database have an option to return only the total count of the records matching 
the specified parameters instead of returning the data frame containing the result.
To activate this option, specify `count = TRUE`:

```{r }
# Fetch the total number of questions put on the government in LegCo in April, 2019
v <- questions(from = "2019-04-01", to = "2019-04-30", count = TRUE)
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```
---

This database is accessible with the following functions/data:

## hansard()

`hansard()` fetches the information of the hansard files. 

```{r }
v <- hansard(from = "2019-02-20", to = "2019-02-20")
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

If `isCEQandA` is `1`, the hansard file is the Record of Proceedings of a Chief Executive's Question
and Answer Session. 

If `isCEQT` is `1`, the hansard file is the Record of Proceedings of a Chief Executive's Question Time.

## legco_section_type

`legco_section_type` is a data frame containing the meaning of the section code.

```{r }
v <- legco_section_type
head(v)
```

## subjects()

`subjects()` fetches all subjects being discussed in a Council meeting. 

```{r eval=FALSE}
# Fetch second reading of bills during the Council meeting on February 20, 2019
v <- subjects(hansard_id = 2714, section_code = "b2r")
head(v)
```
```{r echo=FALSE}
v <- subjects(hansard_id = 2714, section_code = "b2r", to = "2020-03-27")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

The RundownID indicates the starting RundownID of the subject concerned. For instance, the starting 
RundownID of *Smoking (Public Health) (Amendment) Bill 2019* is 899628, meaning that the paragraph text
of this subject is from 899628 to 899649.

If the business is a continuation of a previous meeting, the date of the previous meeting will be shown 
in the field `ResumptionOf`.

## speakers()

`speakers()` fetches the basic information of speakers in LegCo council meetings. 
Speakers here refer to all personnel who can speak during the meetings, which include
not only LegCo members but also government officials and Secretariat staff.

```{r }
# Fetch a list of all speakers in LegCo council meetings
v <- speakers()
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```
```{r }
# Fetch a list of all speakers who are LegCo members
v <- speakers(type = "MB")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```
```{r }
# Look up the details of a speaker with the id 6
speakers(speaker_id = 6)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Every single paragraph in the hansard files (excluding section titles and summoning of bells) is marked
with the unique Speaker ID to indicate the speaker of the text. 

## rundown()

`rundown()` fetches the paragraph text in hansard files. Note that the result is not in any specific order 
so it is necessary to reorder if needed.

```{r eval=FALSE}
# Fetch records of proceedings of the second reading of Smoking (Public Health) (Amendment) Bill 2019
v <- rundown(rundown_id = 899628:899649)
v <- v[order(v$RundownID), ]
rownames(v) <- 1:nrow(v)
v[3:5, ]
```
```{r echo=FALSE}
v <- rundown(rundown_id = 899628:899649, to = "2020-03-27")
v <- v[order(v$RundownID), ]
rownames(v) <- 1:nrow(v)
v[3:5, ]
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Though of little use, BookmarkName can be a useful parameter to search for the necessary data. 
The BookmarkName of the starting Rundown of a subject is a combination of section code and
the sequence number. For instance, the two bills that were under the process of second reading
have a BookmarkName of "b2r01" and "b2r02" respectively. Therefore, it is possible to directly
fetch the starting RundownID of the first bill under second reading on February 20, 2019,
i.e. *Smoking (Public Health) (Amendment) Bill 2019*, by specifying the BookmarkName:

```{r }
# Fetch the first bill under second reading on February 20, 2019
v <- rundown(bookmark_name = "b2r01", from = "2019-02-20", to = "2019-02-20")
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Similarly, it can be applicable on other SectionCode as well, such as "pop01" and "pop02".

## questions()

`questions()` fetches the question put on the government by LegCo members. Note that this function does 
not take HansardID as a filtering parameter.

```{r }
# Fetch questions being put on the government during the Council meeting on February 20, 2019
v <- questions(from = "2019-02-20", to = "2019-02-20")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Similar to the output of `subjects()`, RundownID here refers to the starting RundownID, which can be used 
to determine the range of the full question text.

## bills()

`bills()` fetches bills being debated in LegCo Council meetings.

```{r eval=FALSE}
# Fetch bills debated during the Council meeting on February 20, 2019
v <- bills(hansard_id = 2714)
head(v)
```
```{r echo=FALSE}
v <- bills(hansard_id = 2714, to = "2020-03-27")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Note that the name of a bill may appear more than once like above, since the bill went through first 
and second reading in the same meeting. To fetch more detailed information and key dates of
a particular bill, use `all_bills()` instead.

## motions()

`motions()` fetches the motions discussed in Council meetings. 

```{r eval=FALSE}
# Fetch motions discussed during the Council meeting on February 20, 2019
v <- motions(hansard_id = 2714)
head(v)
```
```{r echo=FALSE}
v <- motions(hansard_id = 2714, to = "2020-03-27")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

Similar to the output of `subjects()` and `questions()`, RundownID here refers to the starting RundownID,
which can be used to determine the range of the full question text.

## petitions()

`petitions()` fetches the petitions raised by LegCo members in Council meetings. 

```{r eval=FALSE}
# Fetch petition laid during the Council meeting on January 19, 2018
v <- petitions(from = "2018-01-10")
v
```
```{r echo=FALSE}
v <- petitions(from = "2018-01-10", to = "2020-03-27")
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

## addresses()

`addresses()` fetches fetches addresses made by members or government officials while presenting papers
to the Council.

```{r eval=FALSE}
# Fetch addresses given during the Council meeting on February 20, 2019
v <- addresses(hansard_id = 2714)
v
```
```{r echo=FALSE}
v <- addresses(hansard_id = 2714, to = "2020-03-27")
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

## statements()

`statements()` fetches statements made by government officials in Council meetings.

```{r eval=FALSE}
# Fetch statements made by government officials during the Council meeting on April 22, 2015
v <- statements(from = "2015-04-22")
v
```
```{r echo=FALSE}
v <- statements(from = "2015-04-22", to = "2020-03-27")
v
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

## voting_results()

`voting_results()` fetches the results of votes conducted in Council meetings. 

```{r eval=FALSE}
# Fetch results of votes conducted during the Council meeting on January 19, 2018
v <- voting_results(hansard_id = 2714)
head(v)
```
```{r echo=FALSE}
v <- voting_results(hansard_id = 2714, to = "2020-03-27")
head(v)
```
```{r echo=FALSE}
change_state()
Sys.sleep(2)
```

`voting_results()` only returns the overall result of the vote. To fetch the voting record of 
individual members, use `voting_record()` instead.

## summoning_bells()

`summoning_bells()` fetches instances in which the summoning bell have been rung in LegCo
Council meetings.

```{r eval=FALSE}
# Fetch instances of summoning bell during the Council meeting on January 19, 2018
v <- summoning_bells(hansard_id = 2714)
head(v)
```
```{r echo=FALSE}
# Fetch instances of summoning bell during the Council meeting on January 19, 2018
v <- summoning_bells(hansard_id = 2714, to = "2020-03-27")
head(v)
```
```{r include=FALSE}
end_vignette()
```
