---
title: "Introduction to legco"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`legco` is an R package to fetch data from the Hong Kong Legislative Council (LegCo) APIs. It provides 
easy access to LegCo's open data in an intergrated manner without having to dig deep into the structures 
and parameters of the APIs. Each function corresponds to a data endpoint of the APIs. Data is retrieved 
in json format and presented in a dataframe. ~~It is recommended to also install the package `legcoplus` 
which provides functions to enhance the usability of the data retrieved from the LegCo APIs.~~

## Installing legco

### From GitHub

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("elgarteo/legco")
```

### Load legco

```{r}
library(legco)
```

## Using legco

### Understanding the LegCo APIs

The LegCo APIs consist of different databases with seperate structures and identifiers,
and each database has its own API. The functions in this package correspond to the various data endpoints
of these APIs. The databases supported by this package and the associating functions are as follow.

1. **Hansard Database**

   <https://www.legco.gov.hk/odata/english/hansard-db.html>
   
   This database contains information on matters discussed in LegCo Council meeting since the fifth term
   of LegCo. Hinting by its name, the database is built upon the PDF hansard files. Relying on the bookmarks 
   and section codes of the hansard files, the data endpoints retrieve data from the files directly. 
   This database is accessible with the following functions:
   
   * `hansard()` fetches the information of the hansard files.
   * `legco_section_type` contains all the section codes used in the hansard files, which are useful in
   extracting information from the hansard files with the function `subjects()`.
   * `subjects()` fetches the subjects in the hansard files, which represent the items in the meeting agenda.
   * `speakers()` fetches the speakers in meetings, including members, government officials and secretariat 
   staff.
   * `rundown()` fetches the full text of the hansard files.
   * `questions()` fetches the questions put on the government by the members during LegCo Council meetings.
   * `bills()` fetches bills that have been debated in LegCo Council meetings. 
   * `motions()` fetches motions that have been debated in LegCo Council meetings.
   * `petitions()` fetches petitions initiated by members in LegCo Council meetings.
   * `addresses()` fetches addresses made by members or government officials before tabling documents in LegCo 
   Council meetings.
   * `statements()` fetches statments made by government officials in LegCo Council meetings.
   * `voting_results()` fetches the results of votes conducted in LegCo Council meetings.
   * `summoning_bells()` fetches instances in which the summoning bell have been rung in LegCo Council meetings.
   
   When using in combination, these functions are essentially hansard files crawler.

1. **Voting Results Database**

   <https://www.legco.gov.hk/odata/english/vrdb.html>
   
   This database contains voting results of the LegCo Council, the House Committee and the Finance Committee
   and its subcomittees starting from the 5th term of LegCo (2012).
   This database is accessible with the following function:
   
   * `voting_record()` fetches the information of votes conducted in the meetings, including the voting 
   record of each member.
   
   While `voting_results()` of the Hansard Database returns only the overall result of votes conducted in 
   Council meetings, `voting_record()` returns much more detailed information of votes conducted in Council 
   and other four committees and subcommittees meetings.
   
1. **Bills Database**

   <https://www.legco.gov.hk/odata/english/billsdb.html>
   
   This database contains key information of all the bills debated in LegCo since 1906. 
   This database is accessible with the following function:
   
   * `all_bills()` fetches the information of bulls that have gone through LegCo.
   
   Comapred to `bills()` of the Hansard Database, `all_bills()` provides much more comprehensive information 
   of bills, including all key dates and the proposer.
   
1. **Meeting Schedule Database**

   <https://www.legco.gov.hk/odata/english/schedule-db.html>
   
   This database contains the member list and the meeting schedule of the LegCo Council and every committee
   since the fifth term of LegCo.
   This database is accessible with the following functions:
   
   * `term()` fetches the terms in LegCo.
   * `session()` fetches the sessions in LegCo.
   * `committee()` fetches a list of LegCo committees. 
   * `membership()` fetches the members of each committee in the form of Member ID.
   * `member()` fetches the members in LegCo. 
   * `member_term()` fetches the terms LegCo members have served in.
   * `meeting()` fetches the meeting schedule of LegCo committees in the form of Meet ID.
   * `meeting_committee()` fetches which committee holds a meeting.
   
   While the purpose of `member()` is similar to `speakers()` of the Hansard Database, `member()` returns only 
   LegCo members. Their identifiers, i.e. Speaker ID and Member ID, are unique and not interchangeable.
   
1. **Attendance Database**

   <https://www.legco.gov.hk/odata/english/attendance-db.html>
   
   This database contains the attendance record of LegCo Council and committee meetings since the sixth term.
   This database is accessible with the following function:
   
   * `attendance()` fetches the attendance of members in LegCo Council and committee meetings.
   
A generic function `legco_api()` is available for access to other databases and endpoints of the LegCo APIs that 
are not specified here.
   
All functions can also be accessed with the prefix `legco_`, e.g. `legco_speakers()` and `speakers()`
return the same result.
   
### Examples

The following code fetches all the LegCo Council meetings held from January 1, 2019 to March 31, 2019.

```{r, echo = TRUE, message = TRUE}
hansard(from = "2019-01-11", to = "2019-03-31")
```

To fetch the business handled during the meeting on February 21, 2019:

```{r, echo = TRUE, message = TRUE}
subjects(hansard_id = 2695)
```

The section codes indicate the type of the business. For example, to look up the type of business of
_Motion on "Increasing transitional housing supply"_:

```{r, echo = TRUE, message = TRUE}
legco_section_type[ifelse("mbm" %in% sapply(legco_section_type$SectionCode,
                                            function(x) unlist(x)), 1, 0), ]
```