---
title: "Introduction to legco"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

`legco` is an R package to fetch data from the Hong Kong Legislative Council (LegCo) APIs. It provides 
easy access to LegCo's open data in an intergrated manner without having to dig deep into the structures 
and parameters of the APIs. Each function corresponds to a data endpoint of the APIs. Data is retrieved 
in json format and presented in a dataframe.

## Installing legco

### From GitHub

```{r, echo = FALSE}
install.packages("devtools")
devtools::install_github("elgarteo/legco")
```

```{r, eval = FALSE, eval = FALSE}
install.packages("https://elgarteo.ga/legco/legco_0.0.9999.tar.gz", repos = NULL, type = "source")
```

### Load legco

```{r}
library(legco)
```

## Understanding the LegCo APIs

The LegCo APIs consist of different databases with seperate structures and identifiers,
and each database has its own API. The functions in this package correspond to the various data endpoints
of these APIs. The databases supported by this package and the associating functions are as follow.

1. **Attendance Database**

   This database contains the attendance record of Council and committee open meetings since the
   sixth term.
   
   This database is accessible with the following function:
   
   * `attendance()` fetches the attendance of members in Council and committee meetings.
   
   See [here](./attn.html) for more information of this database.

1. **Bills Database**

   This database contains key information of all the bills that have been presented in LegCo since 1906. 
   This database is accessible with the following function:
   
   * `all_bills()` fetches the information of bills that have gone through LegCo.
   
   Comapred to `bills()` of the Hansard Database, `all_bills()` provides much more comprehensive information 
   of bills, including all key dates and the proposer.
   
   See [here](./bills.html) for more information of this database.

1. **Hansard Database**

   This database contains information on matters discussed in Council meeting since the fifth term
   of LegCo. Hinting by its name, the database is built upon the PDF hansard files. Relying on the bookmarks 
   and section codes of the hansard files, the data endpoints retrieve data from the files directly. 
   This database is accessible with the following functions/data:
   
   * `hansard()` fetches the information of the hansard files.
   * `legco_section_type` is a data frame that explains that meaning of the section codes used in the
   hansard files.
   * `subjects()` fetches the subjects in the hansard files, which are essentially items in the meeting agenda.
   * `speakers()` fetches the speakers in meetings, including members, government officials and secretariat 
   staff.
   * `rundown()` fetches the full text of the hansard files.
   * `questions()` fetches the questions put on the government by the members during Council meetings.
   * `bills()` fetches bills that have been debated in Council meetings. 
   * `motions()` fetches motions that have been debated in Council meetings.
   * `petitions()` fetches petitions initiated by members in Council meetings.
   * `addresses()` fetches addresses made by members or government officials while presenting papers
   to the Council.
   * `statements()` fetches statments made by government officials in Council meetings.
   * `voting_results()` fetches the results of votes conducted in Council meetings.
   * `summoning_bells()` fetches instances in which the summoning bell have been rung in Council meetings.
   
   When using in combination, these functions are essentially hansard files crawler.
   
   See [here](./hansard.html) for more information of this database.

1. **Meeting Schedule Database**

   This database contains the member list and the meeting schedule of the Council and every committee
   since the fifth term of LegCo.
   This database is accessible with the following functions:
   
   * `term()` fetches the terms in LegCo.
   * `session()` fetches the sessions in LegCo.
   * `committee()` fetches a list of LegCo committees. 
   * `membership()` fetches the members of each committee in the form of Member ID.
   * `member()` fetches the members in LegCo. 
   * `member_term()` fetches the terms LegCo members have served in.
   * `meeting()` fetches the meeting schedule of LegCo committees in the form of Meet ID.
   * `meeting_committee()` fetches which committee holds a meeting.
   
   While the purpose of `member()` is similar to `speakers()` of the Hansard Database, `member()` returns only 
   LegCo members. Their identifiers, i.e. Speaker ID and Member ID, are unique and not interchangeable.
   
   See [here](./schedule.html) for more information of this database.
   
1. **Voting Results Database**

   This database contains voting results of the Council, the House Committee and the Finance Committee
   and its subcomittees starting from the fifth term of LegCo.
   This database is accessible with the following function:
   
   * `voting_record()` fetches the information of votes conducted in the meetings, including the voting 
   record of each member.
   
   While `voting_results()` of the Hansard Database returns only the overall result of votes conducted in 
   Council meetings, `voting_record()` returns much more detailed information of votes conducted in Council 
   and other four committees and subcommittees meetings.
   
   See [here](./voting.html) for more information of this database.
   
---

A generic function `legco_api()` is available for access to other databases and endpoints of the LegCo APIs that 
are not specified here.
   
All functions can also be accessed with the prefix `legco_`, e.g. `legco_speakers()` and `speakers()`
return the same result.

## API Limits

### Request Limit

LegCo APIs have a limit of approximately 1000 requests per IP per hour. Once the limit is reached, you will not be
able to retrieve any data for awhile. If you run into the following error message while pretty sure you have entered
the correct parameters, you have probably reached the limit:

```{r echo = FALSE, message = TRUE, error = TRUE}
# Generate error message by requesting non-existence id
speakers(0)
```

### Node Count Limit

Another limit is the node count limit which is associated with the setting of the LegCo API server.
The limit is at most 100 nodes per request, or approximately 19 filtering conditions in most cases. For instance,
the following code contains 20 filtering conditions and thus reach the node count limit:

```{r }
# A request with 20 filtering conditions
x <- c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19,
       21, 23, 25, 27, 29, 31, 33, 35, 37, 39)
speakers(x)
```

If you run into the error message above, you need to break it down to multiple smaller requests,
like [one of the examples below](#examples).

Note that numeric filtering conditions that are sequential are not subjected to this limit: 

```{r eval = FALSE}
# A request with sequential numeric filtering conditions
x <- c(1:50)
speakers(x)
```

The code above will execute just fine without reaching the node count limit even though it effectively 
contains 50 filtering conditions.

## Examples

The following code shows all the Council meetings held from May 1, 2018 to May 31, 2018.

```{r echo=TRUE, message=FALSE}
hansard(from = "2018-05-01", to = "2018-05-31")
```

To fetch the items on the agenda of the meeting on May 23, 2018:

```{r, echo = TRUE, message = FALSE}
subjects(hansard_id = 2451)
```

In this example, we will look into the motion _Not forgetting the 4 June incident_.

The section codes indicate the type of the business. For exmaple, the section code "mbm" of the
_Not forgetting the 4 June incident_ means that it is a member's motion:

```{r, echo = TRUE, message = FALSE}
legco_section_type[legco_section_type$SectionCode == "mbm", ]
```

The RundownID indicates the location of the first paragraph of the matter concerned in the hansard file. In other words, 
paragraphs of RundownID between 828783 and 828826 (one RundownID prior to the next item on the agenda) are the records of the 
matter the _Not forgetting the 4 june incident_ during the meeting.
The full text of these paragraphs can be fetched by:

```{r, echo = TRUE, message = FALSE}
w <- rundown(id = 828783:828826)
# Order by RundownID, i.e. chronological order
w <- w[order(w$RundownID), ]
rownames(w) <- 1:nrow(w)
# Some two paragraphs of the hansard relevant to the discussion of the motion
w$Content[41:42]
```

To check which members have spoken about the motion and to look up some of their names:

```{r, echo = TRUE, message = TRUE, error = TRUE}
x <- unique(w$SpeakerID[!is.na(w$SpeakerID)])
speakers(id = x)
```

The code above produces 27 filtering conditions which reahces the node count limit.
If you need have parameters longer than that, break them down into multiple requests:

```{r echo=TRUE, message=FALSE}
y1 <- speakers(id = x[1:19])
y2 <- speakers(id = x[20:27])
y <- rbind(y1, y2)
# Show members who have spoken about this motion
head(y[y$Type == "MB", ])
```

To find out the voting results of the motion:

```{r, echo = TRUE, message = FALSE}
v <- voting_results(from = w$MeetingDate[1], to = w$MeetingDate[1], section_code = "mbm")
v[v$Subject == "Not forgetting the 4 June incident", ]
```

It is possible to fetch the detailed voting record of each member on this motion. To get a list of members who voted yes:

```{r, echo = TRUE, message = FALSE}
v <- voting_record(from = w$MeetingDate[1], to = w$MeetingDate[1])
v[v$Vote == "Yes", 32:33]
```

To check the attendance of this meeting:

```{r, echo = TRUE, message = FALSE}
# Find out MeetID of the Council meeting on May 23, 2018
meeting(from = w$MeetingDate[1], to = w$MeetingDate[1])
z <- attendance(meet_id = 126590)
# Show members who were present
z[z$PresentAbsent == "Present", 7:9] 
```
